The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-15 src/ms.tex
First round of full paper edits (#40)
* move defs to preamble and intro tweaks

* re-add python mentions figure, now with total astro yearly paper counts

* remove force to run without cache

* edits up to section 3

* edits through section 3

* edits through section 4

* slightly reorganize end sections

* remove subsubsections for learn

* add new snakemake rule to build affiliated package table

* working affiliated package table, but missing citations

pass through dev key / token

assert and remove except

undo dev key overengineering - it should be fine with the env var

upload ms pdf fi

As defined in \paperii, Astropy affiliated packages are astronomy-related
\python packages that provide functionality that builds upon and extends the
\astropypkg core package that have requested to be included as part of the
Astropy Project community. These packages support the goals and vision of
Astropy of improving code re-use, interoperability, and embracing good coding
practices such as testing and thorough documentation.
All Astropy-coordinated and other affiliated packages are listed with detailed
information on the \href{{https://www.astropy.org/affiliated}}{\astropy
website}; A table summarizing key aspects of the affiliated packages is included
in the Appendix below (Table~\ref{tab:affiliated-registry}).

@@

@@

\begin{longrotatetable}
    \begin{deluxetable*}{ccp{2in}p{2.5in}}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:affiliated-registry}
    \tablehead{
        \colhead{Package Name} &
        % \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer(s)} &
        \colhead{Citation(s)}
      }
      \startdata
        \input{generated/affiliated-table.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}

>>>>

As defined in \paperii, Astropy affiliated packages are astronomy-related
\python packages that provide functionality that builds upon and extends the
\astropypkg core package that have requested to be included as part of the
Astropy Project community. These packages support the goals and vision of
Astropy of improving code re-use, interoperability, and embracing good coding
practices such as testing and thorough documentation.
All Astropy-coordinated and other affiliated packages are listed on the astropy
website.\footnote{\url{https://www.astropy.org/affiliated}}

@@

\todo{APW}{Add a table of all affiliated packages, like in the previous paper}

@@

\begin{longrotatetable}
    \begin{deluxetable*}{ccp{2in}p{2.5in}}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        % \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer(s)} &
        \colhead{Citation(s)}
      }
      \startdata
        \input{generated/affiliated-table.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}
